\documentclass[DIV=15,color=blue!60!green!90]{komacv}

%\usepackage{CormorantGaramond}
\usepackage{quattrocento}
\usepackage{opensans}
\usepackage[light]{Chivo}
\usepackage[T1]{fontenc}

%\addtokomafont{firstnamefont}{\fontfamily{fos}\selectfont\scshape}

\newcommand\HUge{\fontsize{27}{60}\selectfont}

\renewcommand*\firstname{F{\HUge ELIX}\,}
\renewcommand*\familyname{J{\HUge ACKSON}}
\renewcommand*\mobile{+44 7860 582 208}
\renewcommand*\email{naomifaithpyburn@gmail.com}
\renewcommand*\addressstreet{310 Coldhams Lane}
\renewcommand*\addresscity{Cambridge, CB1 3HN}
\renewcommand*\homepage{www.github.com/fojackson8}

\renewcommand\mobilesymbol{\,}

\setlength\dbitemmaincolwidth{12.4em}
\setlength\aftertitlevspace{-2em}
\setlength\hintscolwidth{0.15\textwidth}

\pagestyle{scrheadings}
\clearscrheadfoot

\begin{document}

  \maketitle

  \section{Education}

    \cventry[1em]{2016 -- 2017}{MSci Systems Biology}{University of Cambridge}{}{1 (predicted)}{Modules taken -- Data Handling and Analysis, Modelling and Analysis of Networks, Scientific Computing, Synthetic and Executable Biology.\\Masters thesis -- Adapting a variant calling algorithm to the non-coding regions of\\ the human genome. I am building a new variant caller in Python, and running all scripts\\ on a cloud-based platform by wrapping using Docker. See research link above for details.}
    \cventry[1em]{2013 -- 2016}{BA(Hons) Natural Sciences}{University of Cambridge}{}{2.i (67\%)}{Modules taken --- Maths, Chemistry, Materials Science, Cell and Developmental Biology, Plant and Microbial Sciences, Biochemistry}
    \cventry{2006 -- 2013}{Secondary Education}{Berkhamsted School}{}{}{
    \begin{tabular}{@{}ll}
      A-Level & Maths --- A$^*$, Physics --- A$^*$, Chemistry --- A$^*$, \& Biology --- A \\
      AS-Level & Music --- A \\
      GCSE & 9 A$^*$s, 2 A
    \end{tabular}
    }

  \vspace{-1em}

  \section{Experience}

    \cventry[1em]{Aug -- Present}{Deputy Editor}{Wet Zebra Media}{}{}{Sole paid employee in a digital publishing start-up, requiring fast learning and impeccable organisation and communication. Responsibilities include selecting and editing manuscripts, taking titles through publishing process from submission to print, managing communication with authors, launching social media campaigns and updating accounts daily, organising and hosting events, managing web content, checking legal documents and contracts, training an intern, and writing news articles.}
    \cventry[1em]{Jul -- Aug 2016}{Content Writer}{The SMF Group}{}{}{Produced articles for clients in a digital marketing firm, researching unfamiliar topics, writing efficiently to meet strict deadlines, and editing colleagues' work.}
    \cventry[1em]{Jul -- Sep 2015}{Floor Manager}{The Walrus Room}{}{}{Joined an award-winning London cocktail bar during its launch, as part of a team of just three employees. Trusted with large responsibility from the start, managing invoices, deliveries, stock and streamlining workplace functionality, as well as helping shape the direction of the bar. Contributed creatively to market the bar on social media platforms and on the street.
    }

  \section{Other}

    \cvdoubleitem{Skills}{\small
      \begin{compactitem}
        \item Facilitating discussion
        \item Public speaking
        \item Fluency in Spanish
        \item \LaTeX
      \end{compactitem}}{Interests}{\small\vspace{-1.2em}
      \begin{compactitem}
        \item Feminist theory
        \item Creative home cooking
        \item Blogging
        \item Fairtrade coffee
      \end{compactitem}}

\end{document}
