\documentclass[DIV=15,color=blue!60!green!90]{komacv}

\usepackage{quattrocento}
\usepackage{opensans}
\usepackage[light]{Chivo}
\usepackage[T1]{fontenc}

% \addtokomafont{firstnamefont}{\fontfamily{fos}\selectfont\scshape}

\newcommand\HUge{\fontsize{19}{60}\selectfont}

\renewcommand*\firstname{N{\HUge AOMI}\,}
\renewcommand*\familyname{P{\HUge YBURN}}
\renewcommand*\mobile{+44 7860 582 208}
\renewcommand*\email{naomifaithpyburn@gmail.com}
\renewcommand*\addressstreet{58 Glentham Road}
\renewcommand*\addresscity{London, SW13 9JJ}

\renewcommand\mobilesymbol{\,}

\setlength\dbitemmaincolwidth{12.4em}
\setlength\aftertitlevspace{-2em}
\setlength\hintscolwidth{0.15\textwidth}

\pagestyle{scrheadings}
\clearscrheadfoot

\begin{document}

  \rmfamily

  \maketitle

  \justify
  I am a self-motivated communicator with 5+ years' experience in impact
  storytelling, writing, and editing. I value thinking at a systems level and
  using creative approaches to tackle the problems society faces, most urgently,
  the climate and ecological crisis.

  \raggedright


  \section{Experience}

  \cventry[1em]
  {Apr 2019 -- Present} {Newsletter \& Mass Email Coordinator}
  {Extinction Rebellion (XR)}
  {}
  {}
  {Grew and led a team of 50 volunteers within XR's Media \& Messaging team.
  Grew email list from 20k to 350k global subscribers and developed consistent
  tone of voice. Worked on cross-channel messaging strategy for mass
  participation actions, facilitated group meetings, and collaborated with an
  international team. Supported adoption of self-organising governance systems.
  Helped develop systems to hold conflict within the movement.}

  \cventry[1em]
  {Aug -- Dec 2018} {Writer}
  {Extreme Hotel, Dominican Republic}
  {}
  {}
  {Wrote 100 articles for adventure eco hotel and sustainable aquaponic farm.
  Assisted with marketing and general strategy in a period of significant
  transition.}

  \cventry[1em]
  {Jan 2017 -- Jun 2018}
  {Impact Women Researcher}
  {Ogunt\'e CIC}
  {}
  {}
  {Produced profiles on women social entrepreneurs. Identified and reached out
  to established individuals. Researched, wrote, and edited interviews for
  online publication. Wrote series of blog posts collating findings.}

  \cventry[1em]
  {Jan -- Jul 2017}
  {Chief Writer}
  {Sugarwise}
  {}
  {}
  {Managed the written content and operations at an early-stage food
  certification startup. Liaised with clients and customers to ensure
  satisfaction. Designed graphics for use in marketing materials. Recruited and
  trained new team members. Organised and attended events.}

  \cventry[1em]
  {Aug 2016 -- Feb 2017}
  {Deputy Editor}
  {Wet Zebra Media}
  {}
  {}
  {Sole paid employee in a digital publishing startup, requiring fast learning
  and impeccable organisation. Responsibilities include selecting and editing
  manuscripts, communicating with authors, launching social media campaigns,
  organising and hosting events, managing web content, training interns, and
  writing news articles.}

  % \cventry[1em]
  % {Jul -- Aug 2016}
  % {Content Writer}
  % {The SMF Group}
  % {}
  % {}
  % {Produced articles for clients in a digital marketing firm, researching
  % unfamiliar topics, writing efficiently to meet strict deadlines, and editing
  % colleagues' work.}

  \cventry
  {Jul 2012 -- Jul 2013}
  {Founder \& Editor-in-Chief}
  {INK Student Magazine}
  {}
  {}
  {Co-founded and edited online student publication `INK', which won several
  categories at national Shine Media Awards. Led a team of over 50 students and
  members of staff. First experience of Adobe InDesign. Gained proficiency at
  editing and proofreading, effective people management, and adapting quickly to
  new challenges.}


  \section{Education}

  \cventry[1em]
  {2013 -- 2016}
  {English BA (Hons)}
  {University of Cambridge}
  {}
  {2.i}
  {Developed rigorous work ethic, juggling workload with extra-curricular
  pursuits. Learned the value of precise and concise writing.}

  % \cventry
  % {2006 -- 2013}
  % {Secondary School}
  % {Berkhamsted School}
  % {}
  % {}
  % {
  %   \begin{tabular}{@{}ll}
  %     A-Level & English Literature --- A$^*$, Latin --- A$^*$, History --- A, \& French (AS) --- A\\
  %     GCSE & 11 A$^*$s
  %   \end{tabular}
  % }

\end{document}
