\documentclass[DIV=15,color=blue!60!green!90]{komacv}

%\usepackage{CormorantGaramond}
\usepackage{quattrocento}
\usepackage{opensans}
\usepackage[light]{Chivo}
\usepackage[T1]{fontenc}

%\addtokomafont{firstnamefont}{\fontfamily{fos}\selectfont\scshape}

\newcommand\HUge{\fontsize{19}{60}\selectfont}

\renewcommand*\firstname{N{\HUge AOMI}\,}
\renewcommand*\familyname{P{\HUge YBURN}}
\renewcommand*\mobile{+1 (778) 980-4817}
\renewcommand*\email{naomifaithpyburn@gmail.com}
\renewcommand*\addressstreet{4-2050 Vine Street}
\renewcommand*\addresscity{Vancouver, BC, V6K 3K1}

\renewcommand\mobilesymbol{\,}

\setlength\dbitemmaincolwidth{12.4em}
\setlength\aftertitlevspace{-2em}
\setlength\hintscolwidth{0.15\textwidth}

\pagestyle{scrheadings}
\clearscrheadfoot

\begin{document}

  \rmfamily

  \maketitle

  \justify
  % I am a British young professional with experience working in early-stage startups. I'm eager to learn more about launching tech startups, and to get involved in the entrepreneurial scene in Vancouver.
  I am a British writer with experience in publishing and social enterprise. I’m
  interested in `doing good better' and joining the growing movement to
  make ethical and sustainable business the norm.

  \raggedright

  \vspace{-1em}

  \section{Experience}

    \cventry[0.5em]{Jan 2017 -- Present}{Impact Women Researcher}{Ogunt\'e CIC}{}{}{Produced
      profiles on women social entrepreneurs. Identified and reached out to
      established individuals. Researched, wrote, and edited interviews for
      online publication. Wrote series of blog posts collating findings.}
    \cventry[0.5em]{Jul -- Sep 2017}{Impact Storyteller}{Mongoose
      Energy}{}{}{Researched the economic, social, and environmental impact of
      11 community-owned renewable energy projects managed by Mongoose.
      Conveyed impact findings through written profiles and visually engaging infographics.}
    \cventry[0.5em]{Jan -- Jul 2017}{Chief Writer}{Sugarwise}{}{}{Managed the
      written content and operations at an early-stage food certification
      startup. Wrote articles, government policy consultations, employee
      contracts, formal certification guidelines, client proposals, editorials,
      job advertisements, blog posts, website copy, agendas. Designed graphics
      for use in marketing materials. Recruited and trained new team members.
      Organised and attended events.}
    \cventry[0.5em]{Aug 2016 -- Feb 2017}{Deputy Editor}{Wet Zebra Media}{}{}{Sole paid employee in a digital publishing startup, requiring fast learning and impeccable organisation. Responsibilities include selecting and editing manuscripts, communicating with authors, launching social media campaigns, organising and hosting events, managing web content, checking legal documents, training interns, and writing articles.}
    \cventry[0.5em]{Jul -- Aug 2016}{Content Writer}{The SMF Group}{}{}{Produced articles for clients in a digital marketing firm, researching unfamiliar topics, writing efficiently to meet strict deadlines, and editing colleagues' work.}
    \cventry[0.5em]{Jul 2012 -- Jul 2013}{Founder \& Editor-in-Chief}{INK Student Magazine}{}{}{Co-founded and edited online student publication `INK', which won several categories at national Shine Media Awards. Led a team of over 50 students and members of staff. First experience of Adobe InDesign. Gained proficiency at editing and proofreading, effective people management, adapting quickly to new challenges and public speaking.}

  \vspace{-1em}

  \section{Education}

    \cventry[0.5em]{2013 -- 2016}{English BA (Hons)}{University of Cambridge}{}{2.i}{Honed my command of the English language, learning the value of accuracy and precision in the written word. Developed rigorous work ethic, working autonomously to meet demanding deadlines. Juggling workload with extra-curricular pursuits cultivated excellent time-management abilities.}
    \cventry{2006 -- 2013}{High School}{Berkhamsted School}{}{}{
    \begin{tabular}{@{}ll}
      A-Level & English Literature --- A$^*$, Latin --- A$^*$, History --- A, \& French (AS) --- A\\
      GCSE & 11 A$^*$s
    \end{tabular}
    }

\end{document}
