\documentclass[DIV=15,color=DodgerBlue4]{komacv}

% \usepackage{CormorantGaramond}
\usepackage{quattrocento}
\usepackage{opensans}
\usepackage[light]{Chivo}
\usepackage[T1]{fontenc}

% \addtokomafont{firstnamefont}{\fontfamily{fos}\selectfont\scshape}

\newcommand\HUge{\fontsize{19}{60}\selectfont}

\renewcommand*\firstname{R{\HUge U}\,}
\renewcommand*\familyname{H{\HUge ORLICK}}
\renewcommand*\mobile{+447595302997}
\renewcommand*\email{ruperthorlick@gmail.com}
\renewcommand*\addressstreet{36 Hawthorn Road}
\renewcommand*\addresscity{Godalming, United Kingdom, GU7 2NE}
\renewcommand*\homepage{www.github.com/ruhatch}

\renewcommand\mobilesymbol{\,}
\renewcommand\emailsymbol{\,}

\setlength\dbitemmaincolwidth{12.4em}
\setlength\aftertitlevspace{-2.5em}
\setlength\hintscolwidth{0.15\textwidth}

\pagestyle{scrheadings}
\clearscrheadfoot

\begin{document}

  \rmfamily

  \maketitle

  \justify
  I am a Computer Scientist, Software Engineer, and Environmental Activist with
  experience in functional programming and its mathematical foundations. I also
  have experience facilitating teams and coaching them to adopt self-organising practices.

  \raggedright

  \vspace{-1em}

  \section{Experience}
    \cventry[0.5em]{May 2018 -- Sep 2019}{Senior Haskell
      Developer}{IOHK}{}{}{Worked in a team of four to formalise, implement, and
      property test ledger rules for the Cardano blockchain. Personally designed
      and prototyped a hard-fork combinator to allow seamless transition across
      major protocol updates. Also worked with Head of HR to run a trial of
      Holacracy, a self-organising system, in the organisation. Personally,
      facilitated and implemented Holacracy within the ledger team.}

    \cventry[0.5em]{Dec 2020 -- Present}{Haskell Developer}{Stack
      Builders}{}{}{Completed a three-month project to expose an API for an
      existing software solution. Delivered to client's satisfaction on time and
      on budget.}

    \cventry[0.5em]{May 2019 -- Present}{Organisational Development
      Coach}{Extinction Rebellion}{}{}{Coordinated Self-Organising Systems Team,
      which provided coaching and facilitation to other teams in the movement.
      Designed and delivered several modules in an online training series.
      Coordinated Strategy Stewardship team while running an
      inclusive and participatory strategy process for the UK movement.}

    \cventry[0.5em]{Sep 2017 -- May 2018}{Lead Software
      Developer}{Money\&Co}{}{}{Rebuilt legacy Java codebase using Haskell and
      Nix. Created type-safe APIs for communicating between back and frontends.
      Used GHCJS to compile Haskell to Javascript for frontend. Had control over
      software architecture and development.}

    \cventry[0.5em]{Mar -- Sep 2017}{Software Development Engineer}{Myrtle
      Software}{}{}{Worked on compiling neural networks to FPGAs, using
      Haskell and Nix. Was offered a senior position, including responsibility
      for team productivity.}

    %\cventry[0.5em]{Summer 2016}{Research Intern}{Microsoft Research
      %Cambridge}{}{}{Worked on a project adding functional features to Excel.
      %Presented to managers in Redmond, convincing them to use our research in
      %the next version of Excel.}

  \vspace{-1em}

  \section{Education}

    \cventry[0.5em]{2016 -- 2017}{MEng Computer Science}{University of Cambridge}{}{Distinction}{
      \textit{Thesis:} Formalised the theory of Generalised Species in Homotopy Type
      Theory (HoTT) using Agda. Worked closely with leading researcher in the
      field, who offered me a research position to continue our work. \\
      \vspace{0.3em}
      \textit{Modules:} Category Theory, Multicore Semantics \& Programming, Advanced
      Functional Programming, Distributed Games \& Strategies, Interactive
      Formal Verification.}
    \cventry[0.5em]{2013 -- 2016}{BA Computer Science}{University of
      Cambridge}{}{1st Class (81\%, Rank: 8/81)}{Implemented Path ORAM, a cryptographic
      primitive, in OCaml to search encrypted documents. Analysed performance
      and security properties in a dissertation. Presented ideas to Microsoft
      Research Cambridge.}
%    \cventry[0.5em]{2007 -- 2012}{High School}{St. Paul's School}{}{}{
%    \begin{tabular}{@{}ll}
%      A-Level & Computing --- A$^*$, Maths --- A$^*$, Further Maths --- A$^*$, Physics --- A$^*$ \\
%      AS-Level & Chemistry --- A \\
%      GCSE & 10 A$^*$s, 1 A
%    \end{tabular}
%    }

  \vspace{-1.2em}

  \section{Other}

    \cvdoubleitem{Programming Languages}{\small
      \begin{compactitem}
        \item Haskell, Rust, OCaml, Java
        \item Nix, Isabelle, Agda, Prolog
      \end{compactitem}}{Tools}{\small\vspace{-1.2em}
      \begin{compactitem}
        \item Unix, git, NixOps
        \item Octave, \LaTeX
      \end{compactitem}}

\end{document}
